Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-19 code-tests.tex
updating code test section

Ensuring that a complex piece of software is behaving correctly is a
non-trivial task.  While there are a range of techniques that one can
apply to ensure correctness, the \enzo\ code uses two primary methods:
a suite of test problems that can be compared to previous versions of
the code, to ensure that \enzo\ is, e.g., running correctly on a new
computer, with a new compiler, or after substantial changes have been
made to the code base; and by direct comparisons to other
astrophysical fluid dynamics codes.  We describe the \enzo\ test
methodology in Section~\ref{sec.tests.suite}, code comparisons in
Section~\ref{sec.tests.compare}, and show a small set of
representative test problems in Section~\ref{sec.tests.problems}.

@@

Cosmology: 
Santa Barbara Clusters, \citep{SantaBarbara}.
Enzo-gadget cosmology comparison, \citep{2005ApJS..160....1O}.
Regan et al. Enzo/Gadget Lyman Alpha Forest comparison,
\citep{2007MNRAS.374..196R}.
Heitmann n-body comparison, \citep{2008CS&D....1a5003H}

Hydro:
Agertz hydro comparison, \citep{2007MNRAS.380..963A}.
Tasker test suite, \citep{Tasker2008}.

Turbulence:
Kritsuk supersonic MHD turbulence comparison,
\citep{2011ApJ...737...13K}.  Compares MHD-CT version.

>>>>

Ensuring that a complex piece of software is behaving correctly is a
non-trivial task.  While there are a range of techniques that one can
apply to ensure correctness, the \enzo\ code uses two primary methods:
a suite of test problems that can be compared to previous versions of
the code, to ensure that \enzo\ is, e.g., running correctly on a new
computer, with a new compiler, or after substantial changes have been
made to the code base; and by direct comparisons to other
astrophysical fluid dynamics codes.  We describe the \enzo\ test
methodology in Section~\ref{sec.tests.suite}, code comparisons in
Section~\ref{sec.tests.compare}, and show a small set of
representative test problems in Section~\ref{sec.tests.problems}.  We
further note that the \enzo\ test suite
(Section~\ref{sec.tests.suite}) contains hundreds of test problems, as
well as the ability to compare to a ``gold standard'' solution, and
thus all of the tests shown here are easily reproducible by the
reader.

@@

Cosmology: 
Santa Barbara Clusters, \citep{SantaBarbara}.
Enzo-gadget cosmology comparison, \citep{2005ApJS..160....1O}.
Regan et al. Enzo/Gadget Lyman Alpha Forest comparison,
\citep{2007MNRAS.374..196R}.
Heitmann n-body comparison, \citep{2008CS&D....1a5003H}.
Vazza shock comparison (galaxy clusters), \citep{2011MNRAS.418..960V}.
Voit et al. cluster comparison, \citep{2005MNRAS.364..909V}.

Hydro:
Agertz hydro comparison, \citep{2007MNRAS.380..963A}.
Tasker test suite, \citep{Tasker2008}.
McNally et al. Kelvin-Helmholz test, \citep{2012ApJS..201...18M}.
Robertson et al. Galilean invariance, \citep{2010MNRAS.401.2463R}.

Turbulence:
Kitsionas et al. decaying isothermal supersonic turbulence, \citep{2009A&A...508..541K}.
Kritsuk supersonic MHD turbulence comparison,
\citep{2011ApJ...737...13K}.  Compares MHD-CT version.
